<!--
%\VignetteEngine{rokogiri}
%\VignetteIndexEntry{Getting started with Rokogiri}
-->

# Getting started with Rokogiri

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(rokogiri)
```

Rokogiri is an R package that aims to make it incredibly easy to read
and write XML files from R. It is written in homage to and spirit of
the well-known Ruby gem, [Nokogiri](http://www.nokogiri.org/).

To get started with Rokogiri, load up your R console and try the following 
simple example.

```{r, eval = TRUE}
library(rokogiri)

cat(rokogiri({
  catalog({
    cd({
      tiitle("Empire Burlesque")
      artist("Bob Dylan")
      country("USA")
      company("Columbia")
      price(10.90)
      year(1985)
    })

    cd({
      tiitle("Hide your heart")
      artist("Bonnie Tyler")
      country("UK")
      company("CBS Records")
      price(9.90)
      year(1988)
    })
  })
}))
```

As you can see, the output is the appropriate XML. The advantage of using
Rokogiri over other XML generators is that the code is very readable
to write; it almost looks like English.

If you wish to provide your own XML converter, you can also produce
a list as output.

```{r, eval = TRUE}
rokogiri(output_type = 'list', {
  note({
    to("Tove")
    from("Jani")
    heading("Reminder")
    msg("Don't forget me this weekend!")
  })
})
```

Note that lists in R can share the same name multiple times! This means the list 
produced will not lose multiple records.

```{r, eval = TRUE}
output <- rokogiri(output_type = 'list', {
  note({
    to("Tove")
  })
  note({
    to("Jim")
  })
})
names(output)
```

